Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/methodology.tex
added an amrwind section

\subsubsection{AMR-Wind}
\fxnote{Mike write this part}\\
Describe AMR-Wind

>>>>

\subsubsection{AMR-Wind}

\fxnote{Do we want a github link reference for amr-wind? exawind?}\\

As part of a suite of physics codes within the open-source project called ExaWind, 
AMR-Wind enables more efficient and scalable simulations of wind power plants. 
This is because it is built on top of the AMReX software framework which contains 
all of the functionality needed to develop massively parallel, block-structured 
adaptive mesh refinement (AMR) applications \cite{AMReX_JOSS}.
Since AMR-Wind is limited to Cartesian block-structured grids it is specialized
to handle atmospheric boundary layer physics and wind turbine wakes. 
The block-structured grids enable more efficient algorithms such as 
Multi-Level Multi-Grid (MLMG) \cite{AMReX_JOSS}
and are well suited for next generation supercomputers that use GPU's.

AMR-Wind solves the incompressible Navier-Stokes equations and is generalized to
handle variable density and viscosity. Additionally scalar transport equations can be 
solved such as potential temperature or turbulence models. The discretization in AMR-Wind
is based on the approximate projection method used in IAMR \cite{almgren1998conservative} 
and incflo \cite{sverdrup2018highly}. It is a semi-staggered scheme where the velocity and scalar 
variables are located at cell centers and pressure is located at nodes. Pressure is also staggered
in time so that pressure and the pressure gradient (located at cell centers) are at time $n+1/2$. 
The time discretization is handled with a Crank Nicholson approach where the right hand side 
of the system of equations is evaluated at time $n+1/2$. The advection term is handled explicitly
using an upwind finite-volume method. There are multiple options
within AMR-Wind, but in this paper only the high-order Godunov Piecewise Parabolic 
method (PPM) is used \cite{Colella1984}. The advection terms are projected to face 
centers at $n+1/2$ and are corrected using an exact MAC projection \cite{almgren1998conservative}
which guarantees a divergence free flow. The diffusion terms can be handled explicitly, semi-implicitly, 
or fully implicit and are the discretized using a second-order central difference formula. 
For the simulations in this paper we use a fully implicit scheme as the variable viscosity 
from the eddy viscosity may cause time step restrictions. After the scalar equations
and the momentum equations are advanced in time a nodal projection is used to 
approximately correct the velocity field to make it divergence free. Where the nodal projection
is based on a node centered finite element method \cite{almgren1998conservative}.

%IAMR paper \cite{almgren1998conservative}
%AMReX \cite{AMReX_JOSS}
%incflo \cite{sverdrup2018highly}
%Godunov ppm \cite{Colella1984}
